The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-22 ms.Rmd
tidying up formatting error, switching BioClim to PPM example

Modules are simply R function definitions, with a set of required inputs and outputs.
For example the`Bioclim` module, which uses the `raster` R package [@raster] to download the widely used bioclim [@Hijmans2005] covariate layers in the correct format, is (excluding some error-handling code for brevity) defined as:

```{r bioclimmodule, eval = FALSE}
Bioclim <- function (extent = c(-180, 180, -90, 90),
                     resolution = 10,
                     layers = 1:19) {
    world <- getData('worldclim', var = 'bio', res = resolution)
    world <- world[[layers]]
    cropped <- crop(world, extent(extent))
    return (cropped)
  }
```

This function meets the minimal requirements of a *covariate* module (see Figure \ref{fig:workflows} Panel B); returning a `Raster\*` object of the correct dimensions.

@@

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = &#39;hide&#39;, results = &#39;hide&#39;, message = FALSE, fig.height = 9, fig.width = 9}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap)
```

@@

```{r fengChangeWorkflow, eval = TRUE, fig.show = &#39;hide&#39;}
Feng_Papes_Update <- 
  ChangeWorkflow(workflow = Feng_Papes,
                   output = Chain(InteractiveMap, 
                                  ResponseCurve(cov = 1)))
```

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 300, fig.show = &#39;hide&#39;, fig.height = 3.2}
# combine the printed map and first effect plot

@@

#### Example 2. Evaluating MaxLike

>>>>

Modules are simply R function definitions, with a set of required inputs and outputs.

@@

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = "hide", results = "hide", message = FALSE, fig.height = 9, fig.width = 9}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap)
```

@@

```{r fengChangeWorkflow, eval = TRUE, fig.show = "hide"}
Feng_Papes_Update <- 
  ChangeWorkflow(workflow = Feng_Papes,
                   output = Chain(InteractiveMap, 
                                  ResponseCurve(cov = 1)))
```

```{r combinefengupdate, eval = TRUE, echo = FALSE, dpi = 300, fig.show = "hide", fig.height = 3.2}
# combine the printed map and first effect plot

@@

#### Example 2. Building a point process model module

Recent SDM research has identified an equivalence between MaxEnt and Poisson point process models (PPMs) [] and noted that PPMs can be fitted using Poisson modelling software [Warton & Renner, Renner et al.]. This means that other modelling approaches can be fitted as PPMs, after a bit of data preparation. We illustrate how to build a `zoon` model module by defining a module to fit a PPM using a Generalized Additive Model (GAM).

The code for our model is as follows (see Renner et al., 2014 for details of this approach):

```{r bioclimmodule, eval = FALSE}
PPM_GAM <- function () {
    # to do...
  }
```

The only complicated aspect of this code is construction of a `zoonModel` object, which contains code to make predictions from the model in a standardised way. The other module types do not require this step, so are simpler to implement. The code also meets the minimal requirements of a *model* module, accepting the required argument `.df` and returning the `zoonModel` object.

To convert this code into a ZOON module, we need to write it to a standalone file with the required metadata. the `zoon` function `BuildModule` helps with this step, and can also run checks to make sure we got everything right:

```{r buildmodule, eval = FALSE} 
BuildModule(PPM_GAM, ...)
```

This module can now be used in a `zoon` workflow and shared with others. To upload the module to the `zoon` modules repository, [TBD].

#### Example 3. Evaluating MaxLike
